\subsection{Production Release Process and Capture Reliability}
\label{sec:release-process}

The camera software studied in this work is a privileged, preloaded system application. A capture is not completed by the application alone; it traverses a broad set of shared framework, system-service, vendor, storage, and companion-application components. The exact dependency set varies across features and devices. The important property is that capture is a cross-layer system workflow, rather than an app-local operation. Consequently, a defect found late in development can require coordinated changes to the system binary and a firmware update after release.

\smallskip\noindent\textbf{Continuous validation.}
During active development, the camera team distributes one or more internal builds per day. Each build is exercised by an automated test environment covering supported device and operating-system configurations. Independent product-validation teams and a camera-specialist validation organization additionally test the same build and register reproducible failures. Before a product launch or firmware release, the organization intensifies this process with repeated-capture and memory-pressure scenarios. A release-blocking failure enters a diagnose--fix--retest loop. If the failure cannot be removed before the release gate, the organization restricts the affected behavior under its triggering conditions or removes the new feature from the release.

\smallskip\noindent\textbf{Capture Timeout.}
The product maintains internal performance and reliability KPIs to expose failures before release. One of the highest-priority capture KPIs is \emph{Capture Timeout}. For capture $i$, its timer starts when the request is accepted and stops only after the required frames and metadata have been collected and the first durable image result has been published. The product enforces a fixed deadline, denoted by \deadline{}, while its numeric value is not disclosed. Instrumented development builds surface a deadline violation as a fail-fast diagnostic event, which causes the failure to be registered and investigated instead of remaining as unbounded user-visible latency.

The first durable result is produced by the \emph{Draft Sequence}: a capture-ordered path that stores and publishes an early image before full post-processing completes. Section~\ref{sec:draft-background} explains this path in detail. Because capture is the central camera operation and crosses many software layers, Capture Timeout is a recurrent release-blocking failure with diverse root causes. Parallel capture, introduced to improve shot-to-shot responsiveness, makes this ordered path contend with several active deadlines at once.
