\subsection{A Thermal Threshold Cannot Separate Safe and Unsafe Captures}
\label{sec:guard-limit}

Parallel capture predated the current thermal safeguard. The safeguard was
introduced later, after a Filter-related Capture Timeout on a lower-tier
model at thermal level~4. Because the camera framework shares the policy across
models, the resulting rule disables optional Draft stages at level~4 and above
on flagship devices as well. This static rule is appropriate for containing a
known release incident, but it neither observes the active workload nor the
queue that determines the remaining deadline.

Table~\ref{tab:timeout_index} characterizes the limitation on a
current-generation flagship. For this experiment, we bypassed the deployed
guard and forced either Bokeh alone or Bokeh with Filter throughout 30-shot
portrait bursts. We varied thermal level, output resolution, and memory
pressure, and recorded the first capture that timed out.

\input{tables/tab_timeout_index}

The boundary fails in both directions. It is \emph{under-protective} below
level~4: Bokeh with Filter first times out at capture 29 under normal 24MP
capture even at level~0, and at capture 24 under normal 12MP capture at
level~2. Memory pressure moves failures earlier; for example, at level~3 the
first 24MP Bokeh-plus-Filter timeout moves from capture 12 to capture 5. It is
also \emph{over-restrictive} at and above the boundary. At level~4, the normal
12MP traces complete the first nine captures with Bokeh and Filter and the
first 15 with Bokeh alone, yet the deployed rule disables those stages from
the first capture.

These measurements do not imply that the early captures at level~4 are always
safe. Rather, they show that thermal level is not a sufficient decision
variable: the outcome at one level changes with resolution, memory pressure,
selected stages, and the backlog inherited from previous shots. Thermal state
is useful context for estimating execution time, but no nontrivial scalar
threshold in Table~\ref{tab:timeout_index} separates safe and unsafe captures.
