\subsection{Problem Formulation and Design Requirements}
\label{sec:control-problem}

Let capture $i$ start at time $a_i$, let its Draft Sequence obtain the worker
at time $s_i$, and let \deadline{} be the fixed deadline measured from
$a_i$. The budget remaining when Draft execution starts is

\begin{equation}
  \budget_i = \deadline - (s_i-a_i).
  \label{eq:remaining-budget}
\end{equation}

Let $\admitted_i$ denote the optional stages selected for capture $i$, and let
$\dur_i(\admitted_i)$ be the execution time from Draft start through delivery,
including the required stages and mandatory tail. The capture is deadline-safe
only if

\begin{equation}
  \dur_i(\admitted_i) \leq \budget_i.
  \label{eq:draft-deadline}
\end{equation}

Equation~\ref{eq:draft-deadline} exposes two different control needs.
Admission can reduce $\dur_i(\admitted_i)$ by omitting Bokeh or Filter for
the current capture, but it cannot restore budget already consumed before
$s_i$. Furthermore, if captures arrive faster than the single worker can
complete them, repeated admission decisions alone cannot stop $\budget_i$
from collapsing across the burst. The framework must also control when the next
capture may begin. Delaying the application-facing \texttt{captureAvailable}
callback does not extend the current capture's deadline; it starts the next
capture later, after queued Draft work has progressed, and thereby preserves
more budget for that future capture.

The industrial objective is consequently lexicographic: (1) prevent every
Capture Timeout, because deadline misses are release blocking; (2) retain the
preferred Draft effects on as many captures as the runtime state safely
allows; and (3) minimize added callback delay and its effect on shot-to-shot
responsiveness. Section~\ref{sec:approach} presents the shared tail model and
the coordinated admission and pacing decisions that address these
requirements.
