\subsection{Overview}
\label{sec:overview}

Figure~\ref{fig:controller} shows where the Context-Aware Draft Sequence
Controller sits in the camera stack: inside the camera framework, between
the application and the HAL. The controller leaves the pipeline structure
of Section~\ref{sec:background} unchanged: captures still arrive in parallel,
and Draft Sequences still execute serially on the single Draft worker. What
changes is that every optional Draft stage must now be admitted against the
capture's remaining deadline budget, and every \texttt{captureAvailable}
callback may be briefly held back when the model predicts that starting
another capture would exhaust that budget. Both decisions are driven by one
shared execution-time model.

\input{figures/fig_controller_overview.tex}

The controller reasons about \emph{workloads} rather than nodes: each node
execution on the Draft worker is classified into a workload key that
captures its stage type and cost-relevant context, and each admission
decision concerns an ordered \emph{sequence} of workloads---the planned
suffix from the decision point through the mandatory encode-and-save tail
(Section~\ref{sec:model}). For any such sequence, the model combines
per-workload duration levels with a sequence-level record of past
underprediction to produce a calibrated upper bound on execution time.

A capture proceeds through the controller as follows. When the HAL reports
readiness for the next shot, the pacer decides how long to hold the
callback before the application may capture again (\ding{182},
Section~\ref{sec:pacing}). When the capture's Draft Sequence obtains the
worker, the controller snapshots the capture's remaining budget and
refreshes the pacing state from the model. Before each optional stage
executes, the remaining suffix of the sequence is admitted only if its
upper bound fits the live budget (\ding{183},
Section~\ref{sec:admission}); an admitted optional stage then runs under a
watchdog that reserves budget for the mandatory tail (\ding{184}). At
capture end, the observed stage durations and the resulting sequence
residuals update the model (\ding{185}), closing the loop for subsequent
captures.

Three design decisions shape this architecture. First, \emph{the primary
prediction signal is observed execution history, not device state}. The
framework ships across many device models, where the same thermal level
implies different risk, throttling and frequency scaling are nonlinear, and
a snapshot taken before a stage cannot reflect events during it. Slowdowns
from any of these causes surface directly in observed durations, which the
model tracks; device-state snapshots are still recorded with every
decision, but only for offline analysis
(Section~\ref{sec:implementation}). Second, \emph{one model serves both
control points}. Admission and pacing consume the same per-sequence
estimates, so the work that admission agrees to run is exactly the work
that pacing paces arrivals against, and the two decisions cannot act on
inconsistent views of the pipeline. Third, \emph{the controller introduces
no hand-tuned latency thresholds}. Every decision compares a learned bound
against the existing product deadline \deadline{}; the only fixed
constants are two smoothing parameters of the model itself
(Section~\ref{sec:model}), and no thermal threshold appears anywhere in
the decision path.
