\subsection{A Tail-Calibrated Execution-Time Model}
\label{sec:model}

\smallskip\noindent\textbf{Workload keys and sequences.}
Table~\ref{tab:workload_policy} summarizes the workload taxonomy. Each node
execution is classified by its stage type plus the context that dominates
its cost: every key carries a \emph{size bucket} that snaps the output
resolution to a stable megapixel tier (12, 24, 50, 108, or 200\,MP),
watermark keys carry the watermark type, and encoding keys additionally
carry the image format and request type. Bucketing keeps samples per key
dense enough to learn from, instead of fragmenting them across exact
resolutions. Each key also carries a policy: \emph{optional} work may be
skipped by admission, \emph{required} work always runs and is only
observed, and \emph{reserved} work is the mandatory tail that produces and
stores the Draft image. A decision is always made for a \emph{sequence}
$\sigma = \langle w_1, \ldots, w_m \rangle$, the ordered suffix of planned
workloads from the decision point through the mandatory tail.

\input{tables/tab_workload_policy.tex}

\smallskip\noindent\textbf{Point prediction.}
For each workload key $w$, the model tracks the recent duration level
$\ell(w)$ with an exponentially weighted moving average over observed
durations $t$:
\begin{equation}
  \ell(w) \leftarrow \ell(w) + \alpha_n \bigl( t - \ell(w) \bigr),
  \qquad
  \alpha_n = \max(\alpha_0,\, 1/n),
  \label{eq:ewma}
\end{equation}
where $n$ counts samples for $w$ and $\alpha_0 = 0.3$. The effective step
$\alpha_n$ makes the estimate a plain sample mean for the first few
observations and a responsive tracker afterwards, so slowdowns caused by
throttling, memory pressure, or background load appear in the estimate
without being modeled explicitly. Because some buckets are rare, the
estimate for $w$ consults every same-type sibling key $w'$ that has
samples:
\begin{equation}
  \hat{T}(w) \;=\; \max_{w' \sim w}\;
  \ell(w') \cdot \max\!\left(1,\ \frac{\mathrm{mp}(w)}{\mathrm{mp}(w')}\right),
  \label{eq:crossbucket}
\end{equation}
where $\mathrm{mp}(\cdot)$ is the bucket's megapixel tier. A well-sampled
smaller bucket is scaled \emph{up} by the resolution ratio to bound an
under-sampled larger one, while a slower larger bucket is used as-is and
never scaled down; the scaling is applied at prediction time only, so
buckets never contaminate each other's learned levels. The point
prediction of a sequence is the sum
$P(\sigma) = \sum_{w \in \sigma} \hat{T}(w)$. If no same-type sample
exists at all, $\hat{T}(w) = 0$ and the sequence is handled by the
cold-start rule of Section~\ref{sec:admission}.

\smallskip\noindent\textbf{Sequence residual calibration.}
A point prediction is not sufficient for timeout prevention: the risk that
matters is how far actual durations \emph{exceed} it. After each capture,
the model therefore scores every admission decision it made. Let $p_w$ be
the decision-time prediction for workload $w$ and $t_w$ its observed
duration; the residual score of the decision on $\sigma$ is the log-ratio
\begin{equation}
  s(\sigma) \;=\;
  \max\!\left(0,\
  \ln \frac{\sum_{w \in \sigma} \max(p_w,\, t_w)}{P(\sigma)}\right),
  \label{eq:residual}
\end{equation}
recorded only if every workload in $\sigma$ actually ran. The score is
positive only under underprediction, and the log-ratio form is insensitive
to workload scale. The numerator clamps each workload's contribution to at
least its own prediction, so one stage's overrun cannot be hidden by
another stage's lucky underrun in the same capture. Scores are stored per
decision sequence and in a global pool; at every capture, all sample
weights decay by $\gamma = 0.9$ and negligible samples are pruned, so the
calibration follows the device's recent behavior.

\smallskip\noindent\textbf{Adaptive safety quantile.}
The safety margin applied to a sequence is a high quantile of its residual
scores, chosen adaptively from how much evidence exists. With sample
weights $\omega_j$, the effective sample size and target quantile are
\begin{equation}
  n_{\mathrm{eff}} = \frac{\bigl(\sum_j \omega_j\bigr)^2}{\sum_j \omega_j^2},
  \qquad
  q = 1 - \frac{1}{n_{\mathrm{eff}} + 1},
  \label{eq:quantile}
\end{equation}
and $\hat{s}_q(\sigma)$ is the weighted $q$-quantile of the scores---taken
from the sequence's own samples when any exist and from the global pool
otherwise. Few effective samples yield a modest quantile, avoiding
overtrust of sparse tails; under the decay $\gamma$, the steady-state
effective sample size is $(1+\gamma)/(1-\gamma) = 19$, so a
well-observed sequence is bounded at roughly its 95th percentile of recent
exceedance.

\smallskip\noindent\textbf{Sequence upper bound.}
The raw upper bound of a sequence is
$P(\sigma)\, e^{\hat{s}_q(\sigma)}$: the current duration level times the
calibrated exceedance factor. Because one capture makes decisions at
several stages, the suffixes involved are nested, and independently
calibrated bounds could invert---a longer suffix could appear cheaper than
its own tail. The model therefore computes the bound with a tail-to-head
pass over $\sigma$: writing $\sigma_k = \langle w_k, \ldots, w_m \rangle$,
\begin{equation}
  U(\sigma_k) = \max\!\Bigl(
    P(\sigma_k)\, e^{\hat{s}_q(\sigma_k)},\;
    \hat{T}(w_k) + U(\sigma_{k+1})
  \Bigr),
  \label{eq:ub}
\end{equation}
with $U(\sigma_{m+1}) = 0$ and $U(\sigma) = U(\sigma_1)$. Each suffix's
bound is thus at least its own raw bound and at least its head estimate
plus its tail's bound, so nested bounds are monotone and every admission
decision accounts for at least the full corrected cost of the work that
follows it.
