\subsection{Remaining-Sequence Admission}
\label{sec:admission}

\begin{algorithm}[t]
\caption{Admission at the head of remaining suffix $\sigma$}
\label{alg:admission}
\begin{algorithmic}[1]
\Require suffix $\sigma = \langle w_1, \ldots, w_m \rangle$,
  live budget $b$
\Ensure run or skip for $w_1$; watchdog budget $\tau$
\If{$\mathit{policy}(w_1) \neq \textsc{Optional}$}
  \State \Return \textbf{run} \Comment{required/reserved work always runs}
\EndIf
\State $U \gets 0$;\;\; $P \gets 0$
\For{$k = m$ \textbf{downto} $1$}
  \Comment{tail-to-head walk, Eq.~\eqref{eq:ub}}
  \State $P \gets P + \hat{T}(w_k)$
  \State $U \gets \max\bigl( P \cdot e^{\hat{s}_q(\sigma_k)},\;
    \hat{T}(w_k) + U \bigr)$
\EndFor
\If{$P = 0$}
  \State \Return \textbf{run} \Comment{cold start: admit to observe}
\EndIf
\State $\tau \gets \max\bigl(0,\ b - U(\sigma^{\mathrm{rsv}})\bigr)$
  \Comment{reserve the mandatory tail}
\If{$U \le b$}
  \State \Return \textbf{run} under watchdog $\tau$
\Else
  \State \Return \textbf{skip} $w_1$ and its dependent stages
\EndIf
\end{algorithmic}
\end{algorithm}

The first control point protects the capture that currently owns the Draft
worker. At each decision point, the controller reads the \emph{live}
remaining budget $b$ directly from the capture's timeout clock,
so any budget already consumed by queueing behind earlier captures is
reflected automatically. An optional workload at the head of the planned suffix
$\sigma$ is admitted only if the whole remaining path fits:
\begin{equation}
  \mathit{admit}(\sigma, b)
  \;\iff\;
  P(\sigma) = 0
  \;\;\lor\;\;
  U(\sigma) \le b .
  \label{eq:admit}
\end{equation}
This is precisely the admission question posed in
Section~\ref{sec:control-problem}: not whether the current stage alone is
fast, but whether the queued capture can still finish everything it must
run---including the mandatory tail---before its deadline. The cold-start
disjunct admits sequences the model knows nothing about: a policy that
always skipped unknown workloads could never learn their cost, so the
first executions are admitted to bootstrap observation, after which the
learned bound takes over. Algorithm~\ref{alg:admission} summarizes the
decision.

Admission also respects the structural dependencies among optional stages.
On JPEG inputs, an optional decoding step is the prerequisite of all
downstream YUV effects; it is forced to run when a frame watermark must be
stamped, and conversely, when decoding or the filter is rejected, the
remaining YUV-dependent optional work is skipped as a group while the
mandatory frame watermark is preserved. Because every decision is
conditioned on the full remaining suffix, these per-stage decisions
compose into a consistent degraded path rather than an arbitrary subset of
effects.

Admission is a start-time decision, and it needs a second line of defense:
once a native stage such as Bokeh has started, it cannot be aborted safely
and consumes unrecoverable time if the runtime degrades mid-execution.
Each admitted optional stage therefore runs on a watchdog whose timeout
reserves the calibrated cost of the sequence's reserved workloads
$\sigma^{\mathrm{rsv}}$:
\begin{equation}
  \tau = \max\bigl(0,\ b - U(\sigma^{\mathrm{rsv}})\bigr).
  \label{eq:watchdog}
\end{equation}
If the watchdog expires, the stage's worker is detached and the Draft
Sequence proceeds immediately to the mandatory tail; the stray result is
released when the worker eventually finishes, and pipeline teardown is
deferred until then. The reservation itself is a model decision, so its
outcome feeds the calibration of Section~\ref{sec:model} like any other.
The two mechanisms are complementary: admission prevents optional work
from starting when the remaining path predictably does not fit, while the
watchdog bounds the damage when an admitted stage degrades
unpredictably---by the time a watchdog fires, its budget is already spent,
which is why the watchdog alone is not a viable admission policy.
