\subsection{Capture-Availability Pacing}
\label{sec:pacing}

Admission cannot restore budget a capture has already lost in the queue
(Section~\ref{sec:control-problem}). The second control point therefore
acts on the arrival side: the framework's performance-policy layer
intercepts each \texttt{captureAvailable} callback and releases it to the
application only after a model-derived delay. Delaying the callback does
not extend any running capture's deadline; it lets admitted Draft work
drain before the next capture---and its timeout clock---starts.

Pacing state is refreshed by observation. Every time a Draft Sequence
obtains the worker, the controller snapshots the budget observed at that
draft start, $b^{\mathrm{start}}$, together with the model's
estimates $\bigl(P^{\mathrm{pref}}, U^{\mathrm{pref}}\bigr)$ for the
capture's \emph{preferred path}: the full planned sequence with all
optional stages included. Pacing thus protects the ability to run the
preferred Draft path, not merely a degraded one---consistent with the
lexicographic objective of Section~\ref{sec:control-problem}, which asks
for timeouts to be prevented while retaining as much of the preferred
processing as possible. The snapshot is overwritten at every draft start,
so a fresh burst is paced from its own observed state rather than a stale
trend carried over from the previous burst.

Each callback's delay is the larger of two predicted deficits, using
$[x]^{+} = \max(0, x)$:
\begin{align}
  \delta_{\mathrm{lvl}} &=
    \bigl[\, U^{\mathrm{pref}} - b^{\mathrm{start}} \,\bigr]^{+},
  \label{eq:lvl}\\
  \delta_{\mathrm{bkl}} &=
    \bigl[\, B(t) + U^{\mathrm{pref}} - \deadline \,\bigr]^{+},
  \label{eq:bkl}\\
  \delta &= \max\bigl(\delta_{\mathrm{lvl}},\, \delta_{\mathrm{bkl}}\bigr).
  \label{eq:delay}
\end{align}
The \emph{level deficit} $\delta_{\mathrm{lvl}}$ is the
observation-anchored floor: how much budget the most recent draft start
was short of the preferred path's upper bound. The \emph{backlog deficit}
$\delta_{\mathrm{bkl}}$ accounts for callbacks already released whose
Draft Sequences have not yet started: a backlog clock $B(t)$ tracks their
predicted work, each released callback advances the clock by its own
capture's predicted duration, and each draft start rebases the clock from
the fresh estimate plus the predictions still waiting behind it, so
observation always overrides accumulated prediction. Measuring the
backlog against the deadline \deadline{} itself makes the capture timeout
the burst allowance: an empty pipeline always paces zero, delays appear
only once the allowance is genuinely spent, and callbacks arriving while
a draft is still running are spaced out to the predicted service rate
instead of repeatedly applying one stale correction. The policy contains
no additional tuned constant or threshold---only learned estimates and
the existing deadline.

Pacing state lives only while work is pending: the first capture after
process start is never paced, and the pacer clears itself whenever the
Draft queue fully drains, so isolated shots are never delayed. When a
delay is applied, it postpones the earliest opportunity for the next
shot; this shot-to-shot responsiveness cost is deliberate and explicit.
Every pacing decision is persisted with its applied delay and the inputs
that produced it (Section~\ref{sec:implementation}), so the cost can be
evaluated separately from the deadline-safety benefit rather than hidden
inside end-to-end latency.
