\subsection{Implementation and Observability}
\label{sec:implementation}

We implemented the controller in the capture post-processing layer of a
commercial Android camera framework, in roughly 4\,KLOC of Kotlin
including the observability store and export tooling. The controller
touches the production pipeline at three points. A per-capture profiler is
attached to the Draft node chain: it classifies each executing node into
its workload key, requests the admission decision before the node runs,
arms the watchdog for admitted optional stages, and measures every stage's
duration. The pacer is invoked from the framework's existing
adaptive-performance policy layer, which applies the decided delay to each
\texttt{captureAvailable} callback. Finally, the Draft saving path clears
the pacing state whenever its task queue fully drains. The learned model
is a process-wide singleton shared by all captures, so a burst's early
shots train the bounds its later shots are decided by.

Every decision is persisted with the inputs that produced it: the planned
workload suffix in a canonical string form, the point and upper-bound
predictions, the live budget, the admission outcome, the watchdog budget,
and each pacing decision's applied delay with its level-deficit,
backlog-deficit, and queued-work inputs. Alongside these, the profiler
records per-stage device-state snapshots (thermal level, status, and
headroom; memory and storage pressure), garbage-collection and CPU-time
deltas, and per-stage timeline anchors into an on-device database with a
spreadsheet exporter. Two properties of this store matter for evaluation.
First, planned-but-skipped work appears in the decision records rather
than only executed stages, so admission and pacing policies can be
re-evaluated offline against recorded traces, including counterfactual
variants of the policy. Second, device state is deliberately absent from
the model's inputs (Section~\ref{sec:model}) but present in the records,
which lets us validate offline that the observed-duration signal subsumes
the state a thermal guard would react to.
