\subsection{Experimental Settings}\label{sec:experimental_settings}

\begin{table}[]
    \centering
    \caption{15 benchmark programs across three releases.}
    \label{tab:benchmarks}
    \resizebox{\columnwidth}{!}{%
    \begin{tabular}{l|l|l||l|l|l}
    \toprule \midrule
    \multicolumn{1}{c|}{\textbf{Program}} & \multicolumn{1}{c|}{\textbf{Versions}} & \multicolumn{1}{c||}{\textbf{Branches}} & \multicolumn{1}{c|}{\textbf{Program}} & \multicolumn{1}{c|}{\textbf{Versions}} & \multicolumn{1}{c}{\textbf{Branches}} \\ \midrule \midrule
    bison                                 & 3.6-3.8           & 11.6K-14.0K                            & \multicolumn{1}{l|}{m4}               & \multicolumn{1}{l|}{1.4.18-1.4.20}     & 5.1K-10.9K                            \\ 
    csplit                                & 9.7-9.9           & 6.9K-7.1K                              & \multicolumn{1}{l|}{make}             & \multicolumn{1}{l|}{4.2-4.4}           & 6.4K-7.4K                             \\ 
    diff                                  & 3.10-3.12         & 8.0K-10.0K                             & \multicolumn{1}{l|}{objcopy}          & \multicolumn{1}{l|}{2.43-2.45}         & 30.5K-30.9K                           \\ 
    du                                    & 9.7-9.9           & 6.9K-7.1K                              & \multicolumn{1}{l|}{objdump}          & \multicolumn{1}{l|}{2.43-2.45}         & 43.8K-44.5K                           \\ 
    find                                  & 4.8.0-4.10.0      & 9.0K-12.5K                             & \multicolumn{1}{l|}{patch}            & \multicolumn{1}{l|}{2.6-2.8}           & 5.5K-7.0K                             \\ 
    gawk                                  & 5.3.0-5.3.2       & 19.4K-21.7K                            & \multicolumn{1}{l|}{sqlite}           & \multicolumn{1}{l|}{3.51.0-3.51.2}     & 38.3K-38.8K                           \\ 
    grep                                  & 3.10-3.12         & 7.1K-7.2K                              & \multicolumn{1}{l|}{xorriso}          & \multicolumn{1}{l|}{1.5.2-1.5.6}       & 48.7K-51.6K                           \\ 
    ls                                    & 9.7-9.9           & 8.1K-8.3K                              & \multicolumn{1}{l|}{}                 &                   &                                                            \\ \midrule \bottomrule
    \end{tabular}%
    }
\end{table}

\myparagraph{\bf Baselines}
We compared $\ourtool$ against four baselines: $\default$, $\rerun$, $\seeding$, and $\naive$. $\default$ does not store solving-results and starts exploration from the initial state for each target release. $\rerun$ also starts exploration from the initial state for each target release, but reports the results using the union of test cases generated for the target release and those generated during previous-version testing. $\seeding$ provides concrete seed inputs, which allows symbolic execution to quickly reach states that generate test cases identical to the seed inputs. We provided all test cases generated during previous-version tests as seeds for the target release. $\naive$ skips solver invocations when a newly explored path condition is already stored in the query data, as described in Section~\ref{sec:naive}.


\myparagraph{\bf Benchmarks}
To evaluate the performance of $\ourtool$, we used the 15 open-source C programs. Table~\ref{tab:benchmarks} presents the three consecutive versions of each program and the total number of branches in each version. For a fair evaluation, we first collected C programs in symbolic execution papers published within the past three years and selected only programs whose latest release was published within the past five years. For each program, we ran experiments on the latest three consecutive versions. Across all programs, total branch growth ranges from 0.6\% to 48.1\% on average, showing a diverse benchmark set.

\myparagraph{\bf Other Settings}
For all experiments, we allocated a 12-hour budget to test each version. We repeated each experiment five times under the same setting and reported the average branch coverage. For example, to gather the results in Table~\ref{tab:coverage_main} with a single core, we require 13,500 hours (i.e., 12 hours $\times$ 5 baselines $\times$ 3 releases $\times$ 15 benchmarks $\times$ 5 repetitions). We used Z3-4.15.4~\cite{z32008} as the SMT solver and followed the default option set proposed as optimal by the KLEE developers~\cite{osdiexperiment}.