\section{Introduction}\label{sec:introduction}

Commercial mobile cameras increasingly rely on multi-frame capture and
computationally intensive post-processing to produce a single high-quality
photograph. In the camera framework studied in this paper, the full
post-processing path has been paired from its introduction with a
\emph{draft sequence}. While the full path collects and processes the captured
frames, the draft sequence saves selected input early and publishes a draft
image through the media database. The user can therefore inspect the capture
before final processing finishes, and the framework retains a recovery image
if that processing fails. Once the final result is ready, it replaces the
draft through a database update. The draft sequence is thus a first-class
part of the post-processing architecture, rather than a later workaround for
slow processing.

This architecture has faced a growing tension between image fidelity and
foreground camera responsiveness. As imaging pipelines incorporated more
compute- and memory-intensive processing, executing every full composition
immediately after the shutter began to interfere with interactive camera use,
for example by consuming resources needed by the preview and subsequent
captures. The framework consequently defers full processing for selected
expensive shot modes until the camera application enters the background.
Deferral protects foreground responsiveness, but it also extends the period
during which the draft is the only capture result visible to the user.

The processing performed by the draft sequence therefore evolved together
with the full pipeline. The initial draft path performed no imaging effect;
it encoded and saved an input frame. When effects such as filters and
watermarks made this draft visibly inconsistent with the final result,
lightweight single-frame versions of those effects were added to the draft
sequence. This change exposed a deadline risk. After timeouts clustered at
high overheat levels, an initial production safeguard disabled optional draft
processing at level~5 and above. A later lower-tier device encountered
\emph{Capture Timeout} while applying a draft Filter at level~4, causing the
common threshold to be lowered to~4. The safeguard was a practical response
to a release-blocking failure, but it encoded incidents from earlier devices
and workloads as a fleet-wide threshold. Flagship devices inherited the same
restriction even when they retained enough execution capacity for the
optional work.

The next evolution of portrait processing exposed that this legacy safeguard
could not serve as an enablement policy for a new workload.
Portrait composition was originally performed while the camera application
remained in the foreground, but it was both memory intensive and long
running. Meanwhile, increasingly sophisticated final processing made an
untreated single-frame draft a poor stand-in for the portrait result, in a
shot mode with a particularly visible before--after difference. The framework
therefore attempted to add lightweight multi-frame bokeh to the draft. A
bokeh-bearing draft would provide an approximate portrait result early and,
in turn, allow the heavier final portrait composition to be deferred until
the application enters the background. Despite this architectural change and
the use of lightweight imaging components, Draft Bokeh could not be enabled
in two consecutive flagship generations because Capture Timeout continued to
recur.

Parallel capture is what turns this added draft work into a cumulative
deadline problem. The hardware abstraction layer can report readiness for a
new capture before all frames and draft processing from the preceding capture
have completed. The application may therefore initiate another shot while an
older draft sequence is still running. Draft sequences, however, execute on a
single worker. New sequences queue behind old ones and consume part of their
fixed Capture Timeout budget before their own processing starts. Variability
from thermal throttling, scheduling, memory pressure, and storage can lengthen
one sequence and propagate its delay to the captures behind it. The relevant
risk is consequently the tail latency of the queued and remaining draft work,
not the average latency of an isolated image operation.

The historical guard did not cause this enablement failure: Draft Bokeh also
timed out at levels~1--3, where the guard admits optional work, because the
decision ignores the workload sequence and accumulated queue. Conversely, at
level~4 and above, the guard rejects every optional stage even for early
captures or lighter executions with sufficient budget. Its under-protection
below the threshold and blanket rejection above it show that the guard cannot
serve as an enablement policy for Draft Bokeh. Lowering the threshold improves
safety only by disabling the feature more broadly; raising it improves
availability only by accepting additional timeout risk.

We present a context-aware runtime controller that manages the two quantities
governing a draft deadline. First, a remaining-sequence admission controller
compares the learned upper bound of the current optional stage and all work
after it, including mandatory encoding, with the current capture's remaining
budget. It protects a capture that is already at risk by omitting optional
work whose bound does not fit. Second, a capture-availability pacer delays the
callback that enables a subsequent shot when either the last observed
draft-start budget or the backlog of callback-admitted captures predicts a
deficit. It prevents the same deficit from propagating through a burst. Both
mechanisms consume an online, tail-calibrated upper bound learned from observed
workload execution, rather than a fixed thermal threshold.

Pacing makes the design trade-off explicit. Delaying capture availability can
slow shot-to-shot shooting, whereas admitting too quickly either forces later
stages to be skipped or risks a timeout. Our controller treats deadline safety
as the hard constraint, preserves Draft Bokeh and other optional effects when
the learned budget permits, and applies pacing only for the predicted budget
deficit. We report Capture Timeout, optional-stage availability, and the
applied capture-availability delay separately; observed inter-shot behavior
is an end-to-end effect rather than assumed to equal that delay.

% Evaluation source: tables/tab_eval_data_entry_overrun.tex, normal-capture
% 12MP 30-shot Lv4--Lv6 rows. Reconfirm after the Chapter 4 dataset is frozen.
In the normal 12MP, 30-shot bursts at overheat levels~4--6, where the deployed
guard would disable all optional draft work, the controller completed all 90
captures without a timeout and retained the full preferred draft path for 63
captures (70.0\%). This recovery of Draft functionality incurred a measurable
responsiveness cost: mean applied pacing delay across the three bursts ranged
from 0.85 to 1.15 seconds, with a maximum of 1.50 seconds. These results
demonstrate why safety, draft fidelity, and pacing cost must be considered
together.

\smallskip
\noindent
\myparagraph{Contributions}
We make the following contributions:
\begin{itemize}[leftmargin=*]
  \item \textbf{Industrial problem characterization.} We characterize how a
  fleet-wide guard introduced after a lower-tier Filter failure is
  under-protective and over-restrictive for flagship Draft Bokeh under
  parallel capture.

  \item \textbf{Coordinated runtime control.} We present a controller that
  reuses learned upper bounds at two complementary control points:
  remaining-sequence admission protects the current capture, while
  capture-availability pacing protects subsequent captures from accumulated
  backlog.

  \item \textbf{Industrial prototype evaluation.} We evaluate an
  implementation integrated into a commercial Android camera framework across
  continuous-capture, image-size, memory-pressure, and overheat conditions,
  reporting deadline safety, Draft feature availability, prediction quality,
  and capture-availability pacing cost.
\end{itemize}
