% SeqPAW -- Chapter 2: Preliminaries
% Self-contained: local notation macros are defined here with \providecommand so this
% file does not clash with the ReuSE macros.tex kept for format reference.

\providecommand{\seqpaw}{{\textsc{SeqPaw}}}
\providecommand{\wset}{\ensuremath{\mathcal{W}}}        % universe of workloads
\providecommand{\wl}{\ensuremath{w}}                    % a workload
\providecommand{\wseq}{\ensuremath{s}}                  % a workload sequence (suffix)
\providecommand{\tail}{\ensuremath{\tau}}               % mandatory tail of a sequence
\providecommand{\deadline}{\ensuremath{D}}              % capture deadline (watchdog)
\providecommand{\bgt}{\ensuremath{b}}                   % remaining time budget at a decision
\providecommand{\dur}{\ensuremath{T}}                   % actual execution time
\providecommand{\pdur}{\ensuremath{\widehat{T}}}        % point prediction of execution time
\providecommand{\ub}{\ensuremath{U}}                    % predicted upper bound
\providecommand{\resid}{\ensuremath{r}}                 % log-residual ln(T/\pdur)

\section{Preliminaries}\label{sec:preliminaries}

\subsection{Draft Sequence Execution}\label{sec:dse}

After the shutter fires, a smartphone camera does not save the captured frame
directly. The frame is handed to a post-processing pipeline---which we call a
\emph{draft sequence}---that runs a chain of image-enhancement stages (e.g.,
depth-based bokeh, filters, dynamic effects, and watermarking) before a final
\emph{encoding} stage compresses the result and writes it to storage. We model a
draft sequence as an ordered chain of nodes $\langle n_1, n_2, \dots, n_k\rangle$,
where each node $n_i$ realizes one \emph{workload} $\wl \in \wset$. A workload is the
stable unit of computation whose running time we want to reason about; it is
identified by its operation type and the resolution tier of the frame (a
megapixel bucket), and, for the encoding stage, additionally by the output image
format. Grouping by these attributes keeps the workload key stable across
captures so that timing samples for ``the same work'' accumulate together.

\myparagraph{Deadline and budget}
A capture must finish within a hard real-time \emph{deadline} $\deadline$, enforced
by a capture watchdog. If the pipeline has not produced and saved an image by
$\deadline$, the framework forcibly tears the chain down: the capture is lost or
degraded, a user-visible failure. At any decision point during the sequence, the
relevant quantity is therefore the \emph{remaining budget}
$\bgt = \deadline - t_{\text{now}}$---the wall-clock time still available before the
deadline.

\myparagraph{Workload policies}
Stages are not equally essential, and this asymmetry drives every decision in the
pipeline. We partition workloads into three policies:
\begin{itemize}[leftmargin=*]
  \item \textbf{Mandatory} ($\tail$): the encoding-and-save stage. It must always
        run for the capture to yield any output, and it forms the tail of every
        sequence.
  \item \textbf{Optional}: expensive enhancements (e.g., bokeh, filter) that
        improve the image but may be \emph{skipped} when there is not enough budget
        left to run them without endangering the mandatory tail.
  \item \textbf{Observed}: lightweight stages (e.g., dynamic effects, watermark)
        that always run but whose cost must still be predicted and accounted for,
        since they consume part of the budget the mandatory tail relies on.
\end{itemize}

\myparagraph{Sequences and decisions}
When execution reaches node $n_i$, the work that still remains is the
\emph{suffix} of the chain from $n_i$ onward. We write this as a \emph{workload
sequence} $\wseq = \langle \wl_1, \dots, \wl_m\rangle$, an ordered list of the
remaining workloads, and denote its actual execution time on a given capture by
$\dur(\wseq) = \sum_{j} \dur(\wl_j)$. Crucially, $\dur(\wseq)$ is not fixed: the same
workload runs faster or slower from one capture to the next depending on device
state---thermal throttling as the phone heats up, memory pressure, garbage
collection, and CPU contention---so the pipeline cannot rely on a static cost
table.

At each optional node, two coupled decisions must be made online, \emph{before}
the work runs:
\begin{enumerate}[leftmargin=*]
  \item \textbf{Admission.} Decide whether the remaining suffix $\wseq$ (the optional
        workload plus everything mandatory that follows it) will fit within the
        budget. The stage is admitted only if a predicted upper bound on its
        running time, $\ub(\wseq)$, satisfies $\ub(\wseq) \le \bgt$; otherwise it is
        skipped to protect the mandatory tail and meet the deadline.
  \item \textbf{Watchdog timeout.} An admitted optional workload is run under a
        per-workload timeout so a single overrun cannot starve the tail. The
        timeout reserves enough budget for the mandatory tail $\tail$ and grants the
        rest to the optional workload: $\bgt - \ub(\tail)$. If the workload exceeds
        this, it is detached and cancelled so that encoding still completes within
        $\deadline$.
\end{enumerate}

Algorithm~\ref{alg:decision} summarizes the per-node decision. After the capture
completes, the \emph{actual} per-workload durations become available and are fed
back to refine the predictor (line~9). Learning is thus online, on-device, and
per-device: the model that decides admission for the next capture is exactly the
one updated by the previous ones, with no offline training phase.

\begin{algorithm}[t] \footnotesize
  \caption{Per-node admission and watchdog decision}
  \label{alg:decision}
  \begin{algorithmic}[1]
    \Require remaining suffix $\wseq$, budget $\bgt$, predictor $P$
    \Ensure admit flag, watchdog timeout $\theta$
    \Procedure{Decide}{$\wseq, \bgt, P$}
      \State $\langle \pdur(\wseq),\, \ub(\wseq) \rangle \gets P.\Call{Predict}{\wseq}$
      \If{$\wseq$ has no learned model yet} \Comment{cold start}
        \State $\textit{admit} \gets \textsc{true}$
      \Else
        \State $\textit{admit} \gets (\ub(\wseq) \le \bgt)$
      \EndIf
      \State $\tail \gets$ mandatory tail of $\wseq$
      \State $\theta \gets \max(0,\; \bgt - \ub(\tail))$
      \State \textbf{run} $\wseq$'s head under timeout $\theta$ \textbf{if} \textit{admit}, \textbf{else skip}
      \State \textbf{on capture end:} $P.\Call{Update}{\text{observed } \dur(\wl_j)}$
      \State \Return $\textit{admit},\ \theta$
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

\subsection{Problem Definition}\label{sec:problem}

The pipeline of Section~\ref{sec:dse} reduces to a single learning problem:
predict, online and on-device, an \emph{execution-time upper bound} for a workload
sequence. Captures arrive as a stream $t = 1, 2, \dots$. At a decision point in
capture $t$ we observe a sequence $\wseq_t$ and budget $\bgt_t$ and must emit a point
prediction $\pdur(\wseq_t)$ and an upper bound $\ub(\wseq_t)$ \emph{before} execution;
only afterward do we observe the realized time $\dur(\wseq_t)$. The objective is to
choose $\ub(\cdot)$ that balances two competing goals:

\begin{itemize}[leftmargin=*]
  \item \textbf{Safety.} Under-prediction is the dangerous error: if
        $\dur(\wseq_t) > \ub(\wseq_t)$, an admitted stage can overrun the budget and
        cause a deadline miss or a mandatory-tail watchdog timeout. We therefore
        want $\Pr[\dur(\wseq_t) > \ub(\wseq_t)]$ to stay below a small target. The
        bound is intentionally one-sided.
  \item \textbf{Utility.} An inflated bound is also costly: every millisecond of
        slack $\ub(\wseq_t) - \dur(\wseq_t)$ makes the admission test reject optional
        stages that would in fact have fit, lowering the \emph{admit rate} and
        degrading image quality. A good bound is as tight as safety allows.
\end{itemize}

What makes this hard is the setting in which $\ub(\cdot)$ must be learned. The
predictor runs inside the camera hot path, so it is bound by four constraints
that rule out a conventional offline model:
\begin{itemize}[leftmargin=*]
  \item \textbf{Streaming, bounded cost.} The model updates once per capture in
        near-constant time and bounded memory; there is no batch-retraining loop.
  \item \textbf{Cold start.} It must emit a usable bound from very few---even
        zero---samples for a given sequence, as new devices, new workload variants,
        and rarely seen sequences appear continually.
  \item \textbf{Non-stationarity.} The distribution of $\dur(\wseq_t)$ drifts within a
        session as the device throttles and memory fills. The safety margin cannot
        be a fixed constant; it must self-calibrate to each device's throttling
        magnitude and track drift.
  \item \textbf{Compositionality.} Sequences are nested suffixes that share
        workloads, so their bounds must be mutually consistent (a longer sequence's
        bound should not fall below that of its own suffix), and evidence should be
        shared across sequences that share work.
\end{itemize}

It is convenient to separate the bound into a point estimate and a multiplicative
safety factor, $\ub(\wseq) = \pdur(\wseq)\cdot \exp\!\big(q(\wseq)\big)$, where
$\exp(q(\wseq)) \ge 1$ is driven by the distribution of past \emph{log-residuals}
$\resid = \ln\!\big(\dur / \pdur\big)$. The log-residual is scale-free---it
measures relative over- and under-shoot---so it pools naturally across workloads
of different absolute cost. Section~\ref{sec:naive} shows why the obvious ways of
choosing $\pdur$ and $q$ fail the constraints above, motivating \seqpaw.

\subsection{Limitations of Naive Approaches}\label{sec:naive}

\myparagraph{Static worst-case bounds}
The safest-looking option is to reserve a fixed, offline-profiled worst-case time
for each stage. This trivially satisfies safety but is badly over-conservative:
it assumes a throttled device on every capture, so it skips optional stages even
when the phone is cool and idle. The admit rate collapses, and image quality
suffers, in exactly the common case where the budget was ample. A static table
also cannot follow per-device variation or within-session drift.

\myparagraph{Running mean or last value}
At the other extreme, predicting $\dur(\wseq)$ by a simple average or the last
observed value (with no margin, or a fixed percentage margin) is tight but
unsafe. Such estimators track the \emph{center} of the distribution, not its tail;
under thermal throttling the realized time routinely exceeds them, causing
deadline misses. A fixed percentage margin cannot help, because the right margin
is precisely what differs across devices and thermal states---the quantity that
must be learned.

\myparagraph{Independent per-workload quantiles}
One could bound each workload by its own high quantile and sum them over the
sequence. But summing per-workload tail estimates compounds the margin---each
term already pays for a worst case, and their sum assumes all workloads hit their
worst case simultaneously---yielding a loose, low-utility bound. It also offers no
principled answer for a sequence whose workloads have few or no joint samples
(cold start).

\myparagraph{Offline-trained models}
A model trained offline on logged traces can be accurate at deployment time but
cannot adapt on-device to drift or to a particular handset's throttling profile
without a retraining pipeline, and it still has nothing to say for workload
variants unseen during training. Its cost and its dependence on a training loop
violate the streaming, bounded, cold-start setting of Section~\ref{sec:problem}.

\medskip
\noindent
These failures share a root cause: each fixes one axis---margin, recency,
composition, or adaptivity---while the problem demands all four at once. A usable
bound must be \emph{online} (updated per capture), \emph{self-calibrating} (its
margin learned from observed residuals rather than fixed), \emph{sequence-aware}
(composed consistently over shared workloads, with a cold-start fallback), and
\emph{drift-tracking}. \seqpaw, presented next, is built around these four
requirements.
