\subsection{The Evolving Role of the Draft Sequence}
\label{sec:draft-background}

A shutter event produces multiple image buffers and associated metadata. After
the system collects these inputs, the full post-processing pipeline performs
multi-frame composition and image enhancement, encodes the result, and stores
the final image file. The Draft Sequence complements this pipeline by quickly
producing and publishing an early image while full post-processing continues.
It also retains this early image as a recovery result, ensuring that a captured
photograph can still be saved if final post-processing fails. The Draft image
therefore provides early access to the captured photograph and supports capture
reliability, rather than serving as an internal preview artifact.

As AI-based post-processing in the studied camera system has grown more
sophisticated, its compute and memory demands have increasingly disrupted
camera responsiveness during active use. For some compute-intensive capture
modes, the system therefore defers post-processing until the camera application
switches to the background.
Figure~\ref{fig:draft-pipeline} summarizes this data flow: the captured frames
and metadata feed the Draft Sequence and post-processing pipeline; the Draft
image reaches the user first, and the final image replaces it when deferred
post-processing completes. This deferral keeps the Draft visible for longer,
while the richer final processing can produce visual changes that an untreated
Draft does not reflect; together, these trends make the mismatch more apparent.

The initial Draft Sequence applied no image effects, and single-frame Filter
and Watermark stages were later added to reduce differences between the Draft
and final images. These additions addressed their corresponding effects, but a
conspicuous mismatch remained in portrait capture: background blur appeared
only in the final image. Reducing this mismatch requires extending the portrait
Draft Sequence with lightweight multi-frame composition that approximates the
final Bokeh effect. Consequently, adding lightweight multi-frame composition to
the Draft Sequence poses a substantial engineering challenge.

\input{figures/fig_camera_pipeline.tex}
