\subsection{Industrial Limitations of Static Thermal Gating}
\label{sec:guard-limit}

\smallskip\noindent\textbf{Legacy rationale.}
A Filter-related Capture Timeout on a lower-tier device required a safeguard
that could be deployed across the shared camera framework. Lacking a runtime
predictor that could estimate Draft execution cost consistently across device
models, the product used the already available thermal level as a low-cost risk
indicator. The deployed rule skips optional Draft stages at level~4 and above.
This was a pragmatic release safeguard under the available product constraints,
not an attempt to predict the cost of each capture. Thermal level reflects
system stress, but it does not determine whether a particular Draft Sequence
can complete within its remaining deadline budget.

\smallskip\noindent\textbf{Why static gating fails.}
A thermal-only decision does not encode the enabled Draft stages, resolution,
memory pressure, or capture history. Table~\ref{tab:timeout_index}
characterizes the resulting errors on a current-generation flagship. We
bypassed the deployed guard, forced either Bokeh alone or Bokeh with Filter
throughout 30-shot portrait bursts, varied thermal level, output resolution,
and memory pressure, and recorded the first capture that timed out.

\input{tables/tab_timeout_index}

The fixed boundary errs in both directions. Below level~4, Bokeh alone first
times out at capture~20 under normal 24MP capture at level~3 and at capture~15
under memory pressure; Bokeh with Filter times out even at level~0, at
capture~29 under normal 24MP capture. At level~4, however, the normal 12MP
traces complete the first nine captures with Bokeh and Filter and the first 15
with Bokeh alone before timing out, whereas the deployed rule suppresses both
stages from the first capture. These successful prefixes do not establish that
early level~4 captures are always safe; every forced-on level~4 trace eventually
times out. Rather, the traces provide counterexamples in both directions:
deadline-missing executions below the boundary and deadline-meeting executions
at the boundary. Any cutoff that admits optional work at level~0 admits the
observed level~0 failure, whereas blocking level~0 suppresses optional Draft
work across the entire thermal scale. Retuning the cutoff therefore only shifts
the error between release safety and feature availability.

\smallskip\noindent\textbf{Production consequence.}
Draft Bokeh was evaluated for release in two consecutive flagship generations
but did not ship in either because reproducible Capture Timeouts occurred below
the deployed cutoff. The safeguard did not cause these failures; it remained a
reasonable incident-containment mechanism, but lacked the per-capture
information needed to enable a heavier, queue-sensitive Draft workload. This
repeated enablement failure shows that selecting another global thermal cutoff
is not a viable strategy for Draft Bokeh. Runtime control must instead account
for both the remaining Draft workload and the deadline budget consumed before
that workload begins, which we formalize next.
